Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich A lightweight design to convolution-based deep learning CSI feedback

\cite{li2024lightweight}Proposes GCRNet, a Ghost module-based architecture that reduces feature redundancy in CSI feedback by generating secondary features from primary maps. Achieves 22.15\% lower complexity than \cite{clnet} while maintaining comparable accuracy, addressing efficiency decay in convolution-based methods like \cite{csinet}.

@@

>>>>

\cite{li2024lightweight}Proposes GCRNet, a Ghost module-based architecture that reduces feature redundancy in CSI feedback by generating secondary features from primary maps. Achieves 22.15\% lower complexity than \cite{ji2021clnet} while maintaining comparable accuracy, addressing efficiency decay in convolution-based methods like \cite{abe}.

@@

	\bibitem{ji2021clnet}
	S. Ji and M. Li, ``CLNet: Complex input lightweight neural network designed for massive MIMO CSI feedback,'' \textit{IEEE Wireless Commun. Lett.}, vol. 10, no. 10, pp. 2318--2322, Oct. 2021
